# Getting started with Synapse using R

*Import the synapse R client and log in to Synapse using locally stored credentials. New users have to supply username and password or their Synapse session API key*
```{r}
library(synapseClient)
synapseLogin()
```


#### Start by creating a subfolder in your with an existing folder (could also be project)
```{r}
id = 'syn3156403'   
myFolder = synStore(Folder(name='Analysis', parentId=id))
```


#### Create a wiki for the project and put some text on it:
```{r}
placeholderText = "Place-holder text: Credibly innovate granular internal or organic sources whereas high standards in web-readiness. Energistically scale future-proof core competencies vis-a-vis impactful experiences. Dramatically synthesize integrated schemas with optimal networks."
wiki = WikiPage(owner=myFolder, title="Analysis summary", markdown=placeholderText)
wiki = synStore(wiki)
```

#### See your folder online:
```{r}
#onWeb(myFolder)
```

#### Create and upload a plot to the project:
```{r}
x = rnorm(500,mean=6,sd=4)
y = rnorm(500,mean=2,sd=3)
png(file="demo_plot.png")
par(mfrow = c(1,2))
hist(x, col = "red", xlim = range(-10,15))
hist(y, col = "blue", xlim = range(-10,15))
dev.off()

plotFileEntity = File(path="demo_plot.png", parentId=myFolder$properties$id)
synSetAnnotations(plotFileEntity) = list(sampleType="iPSC", institution="FredHutch", protocol="A43.6")
plotFileEntity = synStore(plotFileEntity)
```



#### Add provenance describing how plot was created:
```{r}
plotFileEntity = synStore(plotFileEntity, 
                          executed='https://github.com/larssono/synapseTutorials/blob/master/R/1.Synapse_R_API_demo.Rmd', 
                          activityName="plot distributions", 
                          activityDescription="Generate histograms for demo",forceVersion=F)
```

#### Upload the full analysis to a Synapse Wiki
```{r}
#library(devtools)
#source_gist("https://gist.github.com/brian-bot/6117476")
#thisFile <- "~/dev/synapseTutorials/R/1.Synapse_R_API_demo.Rmd"
# knit2synapse(thisFile, myProject, overwrite = T)
```

